---
title: "Lifetime lung, breast, and skin cancer \n| brain metastases incidence:\n A
  reproducible SEER-Medicare study\n"
author: ''
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
  pdf_document: default
  html_document: default
header-includes:
- \usepackage[fontsize=12pt]{scrextend}
- \linespread{1.75}
- \usepackage{lineno}
- \renewcommand\linenumberfont{\normalfont\mdseries\scriptsize}
geometry: margin=1in
---

```{r setup, message = FALSE, warning = FALSE, echo = FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::knit_hooks$set(inline = function(x) {
  the_x <- trimws(x,"both")
  if (all(grepl("[0-9]", unlist(strsplit(the_x, split = ""))))) {
    prettyNum(round(as.numeric(the_x),2), big.mark = ",")
  } else {
    x
  }
})

library(pander) 
panderOptions('table.split.table', Inf)
panderOptions('table.emphasize.rownames', TRUE)
panderOptions("big.mark", ",")
panderOptions("table.alignment.default", "left")
set.caption(NULL)

source("analysis/manuscript.R")
source("analysis/figures.R")
source("analysis/abbreviations.R")
```  

\linespread{1.5}
\fontsize{11pt}{11pt}
\selectfont

Mustafa S Ascha^1^, Quinn T Ostrom^2^, James Wright^3^, Jeremy Bordeaux^4^, Andrew Sloan^3^, Frederick Schumacher^5^, Carol Kruchko^6^, Jill S Barnholtz-Sloan^5^

1. 	Center for Clinical Investigation, Department of Population and Quantitative Health Sciences, Case Western Reserve University School of Medicine, Cleveland, Ohio
2.	Baylor College of Medicine, Houston, Texas
3.	University Hospitals Cleveland Medical Center, Department of Neurosurgery, Cleveland, Ohio
4.	University Hospitals Cleveland Medical Center, Department of Dermatology, Cleveland, Ohio
5.	Department of Population and Quantitative Health Sciences, Case Western Reserve University School of Medicine, Cleveland, Ohio
6.  Central Brain Tumor Registry of the United States, Hinsdale, Illinois

\pagebreak

## Abbreviations  

```{r}
pander(abbreviations, split.table = Inf)
```

# Tables

## Table 1: Medicare claims brain metastasis classification accuracy   

```{r classification metrics}
pander(classification_table_to_show)
```   

\pagebreak

## Table 2: Incidence of primary cancer associated with brain metastases  

```{r condensed incidence table}
old_names <- names(ip_aair)
names(ip_aair) <- make.names(old_names, unique = T)
condensed_ip <- map_df(ip_aair, function(x) gsub("\\ \\(.*", "", x))
condensed_ip[["Site"]] <- perma_dupes(condensed_ip[["Site"]])
names(condensed_ip) <- old_names
pander(condensed_ip)
```

\pagebreak

# Figures   

## Figure 1: Data sources and definitions     

```{r}
#library(DiagrammeR)
#mermaid("analysis/data-diagram.mmd")
```

\pagebreak

## Figure 2: Lung and breast cancer incidence proportions of brain metastases by race

```{r, fig.height = 3.5, fig.width = 6.5}
with(the_plots, arrange_plots(lung_race, breast_race))
```

\pagebreak

## Figure 3: Lung and skin cancer incidence proportions by sex

```{r, fig.height = 3.5, fig.width = 6.5}
with(the_plots, arrange_plots(lung_sex, skin_sex))
```

\pagebreak
\linespread{1.2}
\fontsize{10pt}{10pt}
\selectfont

# Supplementary tables

## Supplementary Table 1: Lung cancer demographics and clinical characteristics

```{r lung tableone}
pander_to(table_ones[["lung"]])
```

\pagebreak

## Supplementary Table 2: Breast cancer demographics and clinical characteristics

```{r breast tableone}
pander_to(table_ones[["breast"]])
```

\pagebreak

## Supplementary Table 3: Skin cancer demographics and clinical characteristics

```{r skin tableone}
pander_to(table_ones[["skin"]])
```

\pagebreak

## Supplementary Table 4: Diagnosis code-only algorithms performance   

```{r}
pander(supplementary_classification)
```

\pagebreak

## Supplementary Table 5: Stage-specific incidence proportions   

```{r}
ss_aair %>% 
  select(which_cancer, d_ssg00, inc_p) %>% 
  spread(which_cancer, inc_p) %>% 
  rename(Stage = d_ssg00) %>% 
  pander(split.table = Inf)
```

\pagebreak


